figure sandbox

### 2023-11-07 untargeted/paruntargeted_sandbox.Rmd
Fixed names in manual_typing

parametadata_all <- read_csv("metadata/parametadata.csv") %>% 
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(timepoint=factor(timepoint, levels=paste0("T", c(0,1,3,10,26,73))))
parametadata <- parametadata_all %>%
  filter(polarity==!!polarity) %>%
  filter(amendment==!!amendment) %>%
  filter(IS_type==!!IS_type | samp_type=="Std")
all_stans <- read_csv("metadata/all_stans.csv")

>>>>

parametadata_all <- read_csv("metadata/parametadata.csv") %>% 
  mutate(startime=factor(startime, levels=c("Morn", "Eve"))) %>%
  mutate(depth=factor(depth, levels=c("Surf", "Deep"))) %>%
  mutate(timepoint=factor(timepoint, levels=paste0("T", c(0,1,3,10,26,73))))
parametadata <- parametadata_all %>%
  filter(polarity==!!polarity) %>%
  filter(amendment==!!amendment) %>%
  filter(IS_type==!!IS_type | samp_type=="Std")
manual_typing <- readxl::read_excel("metadata/manual_typing.xlsx") %>%
  mutate(manual_type=ifelse(is.na(manual_type), "Others", manual_type)) %>%
  add_row(compound_name="Thymidine", manual_type="Nucleobases +")
all_stans <- read_csv("metadata/all_stans.csv") %>%
  left_join(manual_typing)
